An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-16 ex3/paper/paper.tex
Added lr/iteration scaling to paper

As \autoref{fig:adv_per_family} shows, for most attack types, most samples can be modified by an adversary to be classified as benign by using \gls{cw}. High accuracy for a particular attack category does not imply that adversarial attacks are  likely to fail for these attacks. Thus we argue that beside the classical metrics such as accuracy, false positives etc., a new metric is needed, which quantifies how easily an \gls{ids} classifier can be fooled.

Such a metric should be easy to compute, easy to interpret and robust with respect to outliers.  We thus propose the \gls{ars}, as the average of the lower half  of minimum distances of adversarial samples. Since \gls{cw} is able to find adversarial samples with minimum distance, the \gls{ars} can be found efficiently as follows: Use \gls{cw} with a small tradeoff to try to generate adversarial samples for an attack type. If more than half of the samples are now wrongly classified, stop. Otherwise increase the tradeoff of \gls{cw} and repeat. If after a predefined number of iterations -- e.g. 100 -- still not more than half of the samples are adversarial, also break.

>>>>

As \autoref{fig:adv_per_family} shows, for most attack types, most samples can be modified by an adversary to be classified as benign by using \gls{cw}. High accuracy for a particular attack category does not imply that adversarial attacks are  likely to fail for these attacks. Thus we argue that beside the classical metrics such as accuracy, false positives etc., a new metric is needed, which quantifies how easily an \gls{ids} classifier can be fooled.
Such a metric should be easy to compute, easy to interpret and robust with respect to outliers.  We thus propose the \gls{ars}, as the average of the lower half  of minimum distances of adversarial samples. Since \gls{cw} is able to find adversarial samples with minimum distance, it can be used for finding the \gls{ars}  efficiently.

When using a large $\epsilon$ in \autoref{eq:carliniWagner}, it is necessary to reduce the gradient descent learning rate  to avoid numerical issues. However, since the distance term is not affected by $\epsilon$, it is necessary to scale the iteration count inversely with the learning rate. \gls{cw} with a large $\epsilon$ therefore needs more time than with a low tradeoff. For neural networks, the \gls{ars} can be efficiently found as follows: Use \gls{cw} with a small tradeoff, trying to generate adversarial samples for an attack type. If more than half of the samples are now wrongly classified, stop. Otherwise increase the tradeoff of \gls{cw} and repeat. If after a predefined number of iterations -- e.g. 100 -- still not more than half of the samples are adversarial, also break.
